\SW Collaboration Publication Policy: CFHT-LS

### 2014-05-16 doc/sw-publication-policy-cfhtls.tex
Typos, Collett added to authors file

\noindent The author categories are grouped according to collaboration membership (defined above). Authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names based on what they have contributed.

@@

Lead authors of \sw papers should circulate drafts to the list of authors (and whoever they wish from the affiliates list) and allow a minimum of two weeks to give time for comments. If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

>>>>

\noindent The author categories are grouped according to collaboration membership (defined above). Authors have either the status to ``opt-out'' or ``opt-in'' on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names based on what they have contributed.

@@

Lead authors of \sw papers should circulate drafts to the list of authors (and whoever they wish from the affiliates list) and allow a minimum of two weeks to give time for comments. If  ``opt-in'' authors have not provided comments within this time frame they will not be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.
